---
title: "Class Reference"
author: "Student name"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
print("Hello Puppy!")
```

## Introduction

Consider this a personal guide to the commands and functions you will learn. In general, when you come across an R command or function that you want to remember, put it in here along with a description of what it does and when you'd use it.

### How to set the working directory

The command to set a working directory is setwd(). For example:

```{r}
setwd("~/Documents/GitHub/data_journalism_2023_spring")
```

### How to install and load the tidyverse

```{r}
install.packages("tidyverse")
library(tidyverse)
```

###How to count rows

###How to read in a CSS file from the internet

You use the 'n()' to count rows, like so 

```{r}
dataframe %>%
  group_by(some_column) %>%
  summarize(count = n())
```



```{r}
wes_moore_contributions <- read_csv("https://raw.githubusercontent.com/stephenneukam/CNS_Annapolis/main/Campaign_finance/Moore_ContributionsList.csv")
```
PRE-LAB 6

Description: Create a new dataframe with population and voter data joined together
```{r}
maryland_population_with_voters <- maryland_population %>% left_join(county_voters_2022)
```

Description for using bind_rows:Combine the four files into a single data frame using the bind_rows function.
```{r}
# bind_rows with list
county_voters_combined <- bind_rows(list(county_voters_2016, county_voters_2018, county_voters_2020, county_voters_2022))
View(county_voters_combined)
```

Description: Using mutate, let's find the county with the highest 18+ Black population as a percentage of all population 18 and over and also the percentage of Democrats in that county
```{r}
maryland_population_with_voters_and_demographics %>%
  mutate(pct_black_18_plus = (pop_black/pop_18_over)*100, pct_dems = (DEM/Total)*100) %>% 
  arrange(desc(pct_black_18_plus)) %>% 
  select(COUNTY, pct_black_18_plus, pct_dems)
```


