---
title: "Reverse Engineering Project"
author: "Dorothy Hood and Samantha Carey"
date: "2023-03-03"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 

In this notebook, we are reverse engineering the story, [Comic Books Are Still Made By Men, For Men And About Men](https://fivethirtyeight.com/features/women-in-comic-books/)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}
options(scipen=999)
library(tidyverse)
library(lubridate)
library(janitor)

```

## Load and Cleaning Data

In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data. 

```{r}
# Load required data
dc_comicbooks <- read_csv("data/dc_comicbooks.csv") %>% 
  clean_names()
# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")
marvel_data <- read_csv("data/marvel_data.csv") %>% 
  clean_names()
# Clean required data and prepare for analysis if needed. 


```

## Sentences to Engineer
In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

* **Sentence text**: "The characters within them are also disproportionately men, as are the new characters introduced each year."
* **Analysis summary**: The results show that 1,967/6,896 characters identify as female characters. This code also provides us information about their sexual identity as some are represented as "homosexual characters". When I changed the filter of sex from female to male, the number if results increased to 4,783/6,896. Through this coode, the findings in the article were correct. The same is true for the marvel data, there are a total of 11,638 male characters and only 3,837 female characters. 

```{r}
# Put code to reverse engineer sentence here
dc_comicbooks %>%
  group_by(sex) %>% 
  summarise(count = n()) %>% 
arrange(desc(count))

# Display results of code below this codeblock
marvel_data %>%
  group_by(sex) %>% 
  summarise(count = n()) %>% 
arrange(desc(count))
```

### Sentence 2

* **Sentence text**: "Females make up about one in four comic book characters."
* **Analysis summary**: This code shows how we combined both data sets into one, allowing us to easily search between the two for results. By grouping the data by sex, and then filtering it by female characters, we are able to see how many there are in total throughout all the data. If you take the total number of female characters, 5,804 and divide it by the total number of characters, 23,272 multiply by 100, you get 24.9 or 25%, which is 1 in 4. So, this then proves what was stated in the sentence. 

```{r}
# Put code to reverse engineer sentence here
total_characters <- nrow(dc_comicbooks) + nrow(marvel_data)
total_characters

dc_and_marvel <- bind_rows(dc_comicbooks, marvel_data)

dc_and_marvel %>% 
  group_by(sex) %>% 
  filter(sex == "Female Characters") %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))
  
# Display results of code below this codeblock

  
```

### Sentence 3

* **Sentence text**: "Of characters with gender data and 100 or more appearances (294 DC characters and 414 Marvel characters), only 29.0 percent of DC’s are female, and a similar 31.1 percent of the Marvel crowd is."

* **Analysis summary**: We first made new data frames to hold each character in each company and if they appeared 100 or more times. In dc_character_appearcount, we can see 294 comic book characters, and in the marvel_character_appearcount, we can see 414. This proves the first part of the sentence. Then, we filtered out from those data frames which characters were females and appeared 100 or more times. In DC, we got 85 characters, and in the Marvel data we got 128. If you take 85 and divide it by 294, then multiply it by 100, you get 28.9%. If you take 128 and divide it by 414 and then multiply it by 100, you get 30.9%. Although not exactly 29.0% and 31.1% like the sentence says, the numbers we got can be rounded and are extremely similar. This proved the sentence. 

```{r}
# Put code to reverse engineer sentence here
dc_character_appearcount <- dc_comicbooks %>% 
  group_by(name, sex) %>% 
  summarise(count = sum(appearances)) %>% 
  filter(count >= 100) %>% 
  arrange(desc(count))

marvel_character_appearcount <- marvel_data %>% 
  group_by(name, sex) %>% 
  summarise(count = sum(appearances)) %>% 
  filter(count >= 100) %>% 
  arrange(desc(count))

dc_character_appearcount  %>% 
  filter(sex == "Female Characters" & count >= 100) %>% 
  group_by(name) %>%
  summarise(count = sum(count)) %>% 
  arrange(desc(count))

marvel_character_appearcount %>% 
  filter(sex == "Female Characters" & count >= 100) %>% 
  group_by(name) %>%
  summarise(count = sum(count)) %>% 
  arrange(desc(count))
# Display results of code below this codeblock

  
```

### Sentence 4

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 5

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

-30-
