---
title: "Reverse Engineering Project"
author: "Dorothy Hood and Samantha Carey"
date: "2023-03-03"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 

In this notebook, we are reverse engineering the story, [Comic Books Are Still Made By Men, For Men And About Men](https://fivethirtyeight.com/features/women-in-comic-books/)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}
options(scipen=999)
library(tidyverse)
library(lubridate)
library(janitor)

```

## Load and Cleaning Data

In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data. 

```{r}
# Load required data
dc_comicbooks <- read_csv("data/dc_comicbooks.csv") %>% 
  clean_names()
# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")
marvel_data <- read_csv("data/marvel_data.csv") %>% 
  clean_names()
# Clean required data and prepare for analysis if needed. 


```

## Sentences to Engineer
In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

* **Sentence text**: "The characters within them are also disproportionately men, as are the new characters introduced each year."
* **Analysis summary**: The results show that 1,967/6,896 characters identify as female characters. This code also provides us information about their sexual identity as some are represented as "homosexual characters". When I changed the filter of sex from female to male, the number if results increased to 4,783/6,896. Through this coode, the findings in the article were correct. The same is true for the marvel data, there are a total of 11,638 male characters and only 3,837 female characters. 

```{r}
# Put code to reverse engineer sentence here
dc_comicbooks %>% 
  filter(sex == "Female Characters") %>% 
  group_by(year) %>% 
arrange(desc(year))

# Display results of code below this codeblock
marvel_data %>% 
  filter(sex == "Female Characters") %>% 
  group_by(year) %>% 
arrange(desc(year))
```

### Sentence 2

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 3

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 4

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 5

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

-30-
